### 2024-02-14 documentation/thesis/thesis_document.tex
.

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field MRI research and
applications, articulates the research question driving this thesis and
delineates the anticipated use cases and benefits that will be explored
and analyzed throughout the study.

@@

Various types of magnets find application in different \gls{mri}
systems. Permanent magnets generate a steady yet relatively weak
magnetic field, electro magnets are energized by electrical currents,
and superconducting electro magnets produce magnetic fields through
electricity and induction. Regardless of the type, the primary objective
is to create a homogeneous magnetic field within the \gls{mri}. The
higher the homogeneity, the more accurate the measurements. This uniform
magnetic field aligns the molecules within the body or object, setting
the stage for a second magnetic system to stimulate these molecules for
measurements.

The challenge with conventional first-order homogeneity systems lies in
their substantial size, weight, and cost. Even when targeting smaller
areas of the body, large devices are often necessary. In response to
this, there is a growing interest in developing low-field \gls{mri}
systems that utilize various magnet types, including permanent magnets.
These systems, while offering advantages in energy efficiency and
reduced complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While incapable of producing images due to lower magnetic
field strength, low-field systems facilitate the comparison of different
field behaviors and the identification of anomalies. O'Reilly and
Teeuwisse and de Gans \cite{OReilly2019-rn} have already
demonstrated low-cost and small-scale implementations with low-field
\gls{mri} in 2021.

Permanent magnets, usually arranged in a circular ``Hallbach array''
around the \gls{mri}, are commonly employed in low-field systems.
However, their drawback is the inherent variability in strength,
complicating the achievement of a homogeneous field and requiring
precise strength information for correct magnet ordering and \gls{mri}
construction.

@@

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1,000 \gls{ppm}.

@@

@@

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri} is the improved
imaging of soft tissues, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \cite{Hori2021-pt}.

Contemporary most \gls{mri} machines employ high-field superconducting
magnets cooled cryogenically, delivering exceptional image resolution.
However, the associated costs, space requirements, and safety
considerations can be substantial. In contrast, permanent magnets
present an economical and space-efficient alternative. Nevertheless,
they generate lower magnetic field strengths, impacting the \gls{snr}
and resulting in lower image resolution within clinically viable scan
times. \cite{Arnold2023-cn}

In response to these challenges, recent endeavors in both academia and
industry aim to leverage the benefits of lower field strength---such as
reduced costs, a smaller device footprint, and diminished safety
concerns---while addressing the inherent drawbacks that compromise image
quality. The optimization of low-field approaches is becoming
increasingly prevalent, tailored to specific clinical inquiries and
contexts.

To overcome limitations associated with lower field strengths, ongoing
research focuses on the meticulous selection and validation of use
cases. This strategic approach is essential for ensuring that the
advantages of lower cost and reduced device size are harnessed without
sacrificing diagnostic accuracy or compromising patient outcomes.
\cite{Arnold2023-cn}

@@

\%\%Example\_hallbach\_ring\_magnet\_with\_cutouts\_for\_eight\_cubical\_permanent\_magnets.png\%\%

Halbach ring magnets \cite{Halbach1980DesignOP} have become a common
design for low field \gls{mri} and \gls{nmr} systems
\cite{cmr.a.20165}.

They have the ability to generate extremely homogeneous magnetic flux
densities, produce virtually no stray fields and are particularly
attractive for larger magnets as their design has the best flux-to-mass
ratio \cite{Wickenbrock_2021}.

A halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
shows an example \gls{cad} model of such a ring, in which in this case
eight cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
generate homogeneous magnetic flux densities of around
\passthrough{\lstinline!20mT!}.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
\end{itemize}

@@

In order to compensate for inhomogeneities in a finished system, there
are various so-called shimming procedures which further improve
homogeneity after the system has been assembled.

@@

@@

@@

\begin{itemize}
\tightlist
\item
  By using binning or sorting algorithms to filter for the most similar
  magnets
\item
  Adjustment of the rotation and position within the Hallbach
  configuration
\end{itemize}

This form of data processing of previously characterized magnetic data
is currently being implemented experimentally in projects using various
algorithms \cite{Wickenbrock_2021}. Standard sorting algorithms are
used as well as specialized algorithms for optimizing homogeneity by
rotating the individual magnets in a Hallbach ring relative to each
other \cite{HalbachMRIDesigner}.

@@

The scope of the software library is to lay the foundation for the
systematic characterization of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customization possible at each step of the process.

The work aims to facilitate magnetic field characterization and improve
the exchange of data between different user groups. Complete
documentation, tutorials and tests will enable users to use the
framework efficiently and adapt it to their specific requirements.

The application of the developed framework for the characterization of
different magnets and the integration of various available magnetic
field sensors serve the practical application and validation of the
developed solution.

This work is divided into six main chapters, which deal with the
approach and implementation. The techniques and concepts used are
explained in detail. Specific examples provide an overview of the
possible use of the developed solution by the user.

Chapter \ref{usecases}. \textbf{Usecases} are the application cases in
which the project is to be used. They illustrate the practical scenarios
and define how the product can be used in the real world. This is
crucial for understanding the needs of the target group and designing
the end result accordingly.

Chapter \ref{evaluation}. \textbf{Evaluation} comprises the systematic
review and assessment of the overall system. This includes the
demonstration of the implemented capabilities of the overall system
against the previously defined usecases.

\hypertarget{usecases}{%
\chapter{Usecases}\label{usecases}}

The following section defines some usecases that the future project
should be able to cover. These illustrate practical situations to
understand the functionality and added value of the implemented solution
for the user.

These were defined in the course of project planning and provide an
overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{evaluation}, the defined usecases are also used as a
reference to demonstrate the implemented capabilities of the solution.

@@

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference \ref{Sensors_(+cli).png} to the user after connecting. The
current measured value can be output using the
\passthrough{\lstinline!readout!} command
\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}
\ref{software-readout-framework}-library. The serial interface is also
used here. However, after a connection attempt by the \gls{hal}
\ref{mrphal} module of the \gls{mrp}
\ref{software-readout-framework}-library, the system switches to binary
mode, which is initiated using the \passthrough{\lstinline!sbm!}
command. The same commands are available as for \gls{cli}-based
communication, but in a binary format.

@@

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These were performed on a
\passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} and
the following software settings:

\begin{itemize}
\tightlist
\item
  Raspberry Pi OS Lite - \gls{os}
  \passthrough{\lstinline!debian bookworm x64!},
\item
  \gls{mrp} \ref{software-readout-framework}-library - Version
  \passthrough{\lstinline!1.4.1!}
\item
  Unified Sensor \ref{unified-sensor}-firmware - Version
  \passthrough{\lstinline!1.0.1!}
\end{itemize}

It can be seen that a jitter time of up to an additional
\passthrough{\lstinline!1ms!} is added between the triggering of the
measurements by the host system and the receipt of the command by the
sensor hardware. If the host system is still under load, this value
increases many times over. This means that synchronising several sensors
via the \gls{usb} connection alone is not sufficient.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received.

Since the presumed \passthrough{\lstinline!primary!} sensor cannot
register its own sync pulse (because the pin is switched to output),
there is a timeout branch condition
\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
\passthrough{\lstinline!primary!} sensor. This means that in a chain of
sensors there is exactly one \passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors.

In single-sensor operation, this automatically jumps to
\passthrough{\lstinline!primary!} sensor operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the \passthrough{\lstinline!opmode!}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here was that there is no numbering or sequence of the
individual sensors.

@@

These cover all the required functions described in the usecases
\ref{usecases}. The most important difference, apart from the sensor
used, is the \passthrough{\lstinline!scan mode!}. In this context, this
describes whether the sensor can measure a
\passthrough{\lstinline!static!} fixed point on the magnet or if the
sensor can move \passthrough{\lstinline!dynamically!} around the magnet
using a controllable manipulator.

In the following, the hardware structure of a
\passthrough{\lstinline!static!} and \passthrough{\lstinline!dynamic!}
sensor is described. For the \passthrough{\lstinline!static!} sensor,
only the \passthrough{\lstinline!1D!} variant is shown, as this does not
differ significantly from the structure of the
\passthrough{\lstinline!1D: dual sensor!}, except it uses two
\passthrough{\lstinline!TLV493D!} sensors, mounted above and on top of
the magnet.

@@

The electrical level here is based on a
\passthrough{\lstinline!Raspberry-Pi Pico!} together with the
\passthrough{\lstinline!MMC5603NJ!} magnetic sensor. The mechanical
setup consists of four 3D printed components, which are fixed together
with nylon screws to minimise possible influences on the measurement.

Since the \passthrough{\lstinline!MMC5603NJ!} only has limited
measurement range of total 6uT, even small coin sized neodymium magnets
already saturates the sensor. It is possible to mount 3D printed spacers
over the sensor to increase the distance between the magnet and the
sensor and thus also measure these magnets.

@@

On the electrical side, it also consists of a
\passthrough{\lstinline!SKR-Pico!} stepper motor controller, together
with the \passthrough{\lstinline!TLV493D!} magnetic field sensor. This
was chosen because of its larger measuring range and can therefore be
used more universally without having to change the sensor of the arm.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of 0T to 3T with a resolution of
0.1mT. It offers an RS232 interface with a documented protocol for
connection to a \gls{pc}.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical RS232 interface. As with the other sensors, this
interface consists of your \passthrough{\lstinline!Raspberry-Pi Pico!}
with an additional level shifter.

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol of the
sensor was implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

As the following, this concept is referred to as
\passthrough{\lstinline!user interaction points!}
\ref{user-interaction-points} and is explained in the following chapter.

@@

The following example shows the advantages of using the
\passthrough{\lstinline!User interaction points!}:

>>>>

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field MRI research and
applications, articulates the research question driving this thesis and
delineates the anticipated usecases and benefits that will be explored
and analyzed throughout the study.

@@

Various types of magnets find application in different \gls{mri}
systems. Permanent magnets generate a steady yet relatively weak
magnetic field, electro magnets are energized by electrical currents,
and superconducting electro magnets produce magnetic fields through
electric induction. Regardless of the type, the primary objective is to
create a homogeneous magnetic field within the \gls{mri}. The higher the
homogeneity, the more accurate the measurements. This uniform magnetic
field aligns the molecules within the body or object, setting the stage
for a second magnetic system to stimulate these molecules for
spin-measurements.

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary. In response to this, there
is a growing interest in developing low-field \gls{mri} systems that
utilize various magnet types, including permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While incapable of producing images due to lower magnetic
field strength, low-field systems facilitate the comparison of different
field behaviors and the identification of anomalies. O'Reilly and
Teeuwisse and de Gans \cite{OReilly2019-rn} have already
demonstrated low-cost and small-scale implementations with low-field
\gls{mri} in 2021.

Permanent magnets, usually arranged in a circular ``Halbach array''
around the \gls{mri}, are commonly employed in low-field systems.
However, their drawback is the inherent variability in strength,
complicating the achievement of a homogeneous field and requiring
precise strength information for correct magnet ordering and \gls{mri}
construction. Completed MRI systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment becomes formidable. An approach dictates that meticulous
adjustments to the magnets should be undertaken proactively, prior to
the finalization of the MRI system.

@@

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1,000 \gls{ppm}. In the end, the sensors should
also measure how uniform the magnetic field is in a completed \gls{mri}
system.

@@

In the realm of modern medical imaging, high-field superconducting
magnets dominate most \gls{mri} machines, providing high blac-withe
image resolution. However, the substantial costs, space prerequisites,
and safety considerations associated with these systems pose
considerable challenges.

Magnetic resonance imaging \gls{mri} relies on the presence of a robust
magnetic field, and over time, there has been a continual push to
enhance the strength of these magnetic fields. This strength is
quantified in units of Tesla {[}T{]}, commonly referred to as the B0
field in medical contexts, while physicists use the term magnetic field
induction. The \gls{snr} is proprtional to the magnetic B0 field;
growing magnetic field leads automatically to higher \gls{snr}.

Notably, the focus on high-field systems predominated discussions until
around 1991 when the possibility of constructing \gls{mri} machines with
lower magnetic field strengths began to emerge. This marked a pivotal
shift in exploring the potential advantages and applications of
low-field \gls{mri} systems. \cite{Nitz2016}

@@

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri} is the improved
imaging of soft tissues, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \cite{Hori2021-pt}, cost reduction, a smaller device
footprint, alleviated safety concerns and leading to diminished image
resolution within clinically feasible scan durations.
\cite{Arnold2023-cn}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to 0.35 Tesla can be generated. However, this
achievement comes at the cost of an average system weight of 14 tons.
Despite their cost-effectiveness in production and maintenance,
permanent magnets exhibit drawbacks such as high temperature dependence
and a limited \gls{snr} due to the constrained field strength.
\cite{Nitz2016}

In particular, the advantages of the small design, the fast and simple
image acquisition and the low costs are advantages that will become
increasingly important in the future. However, the use of permanent
magnets and their structure is particularly important in such systems
and need to be analysed.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}
\caption{Example Hallbach ring with cutouts for eight magnets
\label{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}}
\end{figure}

The positioning of permanent magnets holds a pivotal role in
constructing an MRI and influencing the homogeneity of the B0 magnetic
field. Halbach ring magnets \cite{Halbach1980DesignOP} have become a
common design for low field \gls{mri} and \gls{nmr} systems
\cite{cmr.a.20165}.

This positioning has the ability to generate extremely homogeneous
magnetic flux densities, produce virtually no stray fields and is
particularly attractive for larger magnets as their design has the best
flux-to-mass ratio \cite{Wickenbrock_2021}.

A halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring, in which in this case eight
cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
generate homogeneous magnetic flux densities of around
\passthrough{\lstinline!20mT!}.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
  \cite{inbook}
\end{itemize}

@@

Halbach magnetic arrays present a compelling choice for mobile NMR due
to their ability to produce highly homogeneous and robust magnetic
fields per unit of magnetic mass, coupled with minimal stray fields. The
term ``Halbach Array'' (commonly known as ``magic rings'') denotes a
precise configuration of permanent magnets designed to amplify magnetic
flux on one side while concurrently mitigating or eliminating it on the
opposite side. \cite{inbook}

The Halbach magnetic array emerges as a crucial element for future
Magnet Characterization. Given that this thesis centers on assessing the
sensors' applicability, the Halbach magnetic array serves as a tool for
measurements, although its implementation and further discussion will
not be the primary focus.

In order to compensate for inhomogeneities in a finished system, there
are various so-called shimming procedures which further improve
homogeneity after the system has been assembled. This procedure is
explained in the following chapter.

@@

Optimal homogeneity is attained through intricate designs facilitating
active shimming, a technique crucial for achieving high-resolution
spectroscopy. Beyond this, simpler combinations and adaptations of
Halbach rings offer versatility, making them suitable for variable field
magnets or magnets that can be effortlessly opened without applying
force. \cite{inbook}

@@

\textbf{Low-Field MRI}

According to Wolfgang R. Nitz in 2016, just 13.4\% of actively used v
systems are low-field \gls{mri} (66.6\% 1.5T systems, 20\% 3.0 T system,
14.4\% low field with \textless0.5T). {[}Nitz2016{]} Nitz also
highlights that presently, the landscape of \gls{mri} technology is
dominated by a single manufacturer dealing with resistive magnets,
namely Stand-up \gls{mri} from FONAR Corp.~In contrast, the industry
giants such as Siemens, General Electric, Philips, Toshiba, among
others, predominantly rely on either permanent magnets or
superconducting magnets in their \gls{mri} systems. This notable
concentration underscores the distinctive position of Stand-up \gls{mri}
as a trailblazer in utilizing resistive magnets within the competitive
realm of magnetic resonance imaging. {[}Nitz2016{]}

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous 27 cm diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019. This innovative setup was
subsequently employed in 2020 to acquire in vivo MR images, showcasing
the practical applications of their pioneering research
\cite{OReilly2021-ep}. 2023 veröffentlichten de Vos, Remis und Webb
eine zusammenfassung zur gestaltng eines oint-of-care halbach array
low-field \gls{mri} system \cite{De_Vos2023-pb}.

The objective of this \gls{mri} system is to prioritize
cost-effectiveness while efficiently capturing low-frequency images of
the head. The emphasis lies on swift and accurate imaging, achieved
through a streamlined approach that favors simplicity in the resultant
images. This \gls{mri} system is strategically designed with a primary
focus on cost-effectiveness, aiming to efficiently capture low-frequency
images of the head. The overarching goal is to achieve rapid and
accurate imaging through a simplified approach, prioritizing clarity and
ease in the resulting images.

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
B0 field strength of 50.4 mT, and an impressive homogeneity of 2400 ppm
over a 20cm diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This
exceptional homogeneity enables the utilization of coil-based gradients
for spatial encoding, significantly enhancing the flexibility of image
acquisition.

To further refine the magnet's homogeneity, optimization techniques are
employed by adjusting the radius of the Halbach cylinder along the
length of the magnet. The deliberate choice of smaller magnets, as
opposed to other Halbach designs, serves to compensate for inherent
manufacturing imperfections in each individual magnet. This strategic
decision not only mitigates structural demands on the magnet housing in
terms of strength and weight but also augments safety throughout the
construction process.

\textbf{Magnet Characerisation}

@@

\begin{itemize}
\tightlist
\item
  By using binning or sorting algorithms to filter for the most similar
  magnets
\item
  Adjustment of the rotation and position within the Halbach
  configuration
\end{itemize}

This form of data processing of previously characterised magnetic data
is currently being implemented experimentally in projects using various
algorithms \cite{Wickenbrock_2021}. Standard sorting algorithms are
used as well as specialized algorithms for optimizing homogeneity by
rotating the individual magnets in a Halbach ring relative to each other
\cite{HalbachMRIDesigner}.

@@

Within the framework of the ``DeLoRI'' (Dedicated Low-field \gls{mri}
for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
crafting a compact and mobile low-field \gls{mri} unit tailored
specifically for screening purposes. As described since 1991 low-field
\gls{mri}s have evolved into a burgeoning realm of research, showcasing
substantial promise within the field of medical technology. The endeavor
by Fraunhofer MEVIS exemplifies the ongoing commitment to harnessing the
potential of low-field \gls{mri} for enhanced breast screening
applications.

The focus of the ongoing efforts is to enhance the homogeneity of
magnets within low-field MRI systems below 1.000ppm, primarily driven by
the goal of establishing a compact low-field \gls{mri} for breast cancer
detection.

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field MRI system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging AI-based methodologies.

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, DeLoRI aims to design an open \gls{mri},
departing from the circular \gls{mri} configuration discussed in the
publication. This innovation is geared towards streamlining breast
examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation. In addition DeLoRI endeavors
to achieve heightened accuracy, striving for precision levels below
1,000 ppm. While O'Reilly, Teeuwisse, and Webb were able to modify the
ring diameter to influence field homogeneity, the unique goal here is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This nuanced approach aims
to provide insights into magnetic field uniformity before the magnets
are integrated, thereby streamlining the optimization process.
Furthermore,

It is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterization process.

To achieve this, a versatile hardware setup is in development, designed
to accommodate various sensors for the measurement of magnets or other
objects. Simultaneously, a software interface is being crafted to
universally read data from different sensors and interact seamlessly
with the diverse firmware associated with various Halbach sensors. A key
feature of this system is the ease of sensor interchangeability,
facilitating adaptability and versatility in the characterization
process.

The scope of the software library is to lay the foundation for the
systematic characterisation of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customization possible at each step of the process.
Complete documentation, tutorials and tests will enable users to use the
framework efficiently and adapt it to their specific requirements.

The application of the developed framework for the characterisation of
different magnets and the integration of various available magnetic
field sensors serve the practical application and validation of the
developed solution.

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of 1,000 ppm.
Furthermore, the study seeks to validate whether the measuring range of
these sensors appropriately corresponds to the required field strength,
ensuring their suitability for the intended application.

\hypertarget{research-question-and-approach}{%
\section{Research Question and
Approach}\label{research-question-and-approach}}

Concerning the DeLoRI project, this study exclusively delves into the
realm of permanent magnets employed for creating a homogeneous B0 field
through Halbach rings. Other systems and spin generation for
measurements are deliberately excluded from consideration but will be
necessary in later stages of the DeLoRI project.

The primary objectives of this work revolve around addressing two
pivotal research questions:

\begin{itemize}
\item
  Sensor Characterization: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than 1,000 ppm? The desired outcome is a
  measurement of less than 50 \(\mu\)T at 1,000 ppm, with a specific
  focus on determining the sensors' viability for noise measurements.
\end{itemize}

It is crucial to emphasize that the intention is not to characterize the
magnets per se; rather, the emphasis lies in deriving meaningful
insights about the sensors deployed.

This work distinctly prioritizes the development of both hardware and
software tailored for sensor utilization and final testing. Physical
properties and considerations take a secondary role in comparison to the
overarching goal of refining the sensor-based methodologies.

\hypertarget{usecases}{%
\section{Usecases}\label{usecases}}

The following section defines some usecases that the future project
should be able to cover. These usecases define the setup of the hard-
and software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The usecases were defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{usecase-evaluation}, the defined usecases are also used as
a reference to demonstrate the implemented capabilities of the solution.
This is crucial for understanding the needs of the target group and
designing the end result accordingly.

@@

This work is divided into six main chapters, which deal with the
approach, implementation and evaluation. The techniques and concepts
used are explained in detail. Specific examples provide an overview of
the possible use of the developed solution by the user.

Chapter \ref{usecase-evaluation}. \textbf{Usecase Evaluation} describes
the application of the framework to the previously defined usecases and
thus forms the basis for later evaluation.

Chapter \ref{evaluation}. \textbf{Evaluation} outlines the evaluation
process for permanent magnets using the developed framework. The
research questions posed regarding the suitability of the sensors used
for the characterisation of permanent magnets are examined.

Chapter \ref{conclusion-and-discussion}. \textbf{Conclusion and
Discussion} bringing together essential research components, it
synthesizes study outcomes, discusses implications, and provides
insights for future work. This section ensures closure and aids readers
in grasping the broader context and significance of the research.

Finally, a comprehensive hardware and software framework must be
established, capable of measuring diverse objects using various sensors.
Additionally, conclusive remarks should be provided regarding the
suitability of the employed sensors for magnetic field measurements.

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference \ref{Sensors_(+cli).png} to the user after connecting. The
current measured value can be output using the \emph{readout} command
\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}
\ref{software-readout-framework}-library. The serial interface is also
used here. However, after a connection attempt by the \gls{hal}
\ref{mrphal} module of the \gls{mrp}
\ref{software-readout-framework}-library, the system switches to binary
mode, which is initiated using the \emph{sbm} command. The same commands
are available as for \gls{cli}-based communication, but in a binary
format.

@@

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These were performed on a
\emph{RaspberryPi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
Sensor} \ref{d-single-sensor} and the following software settings:

\begin{itemize}
\tightlist
\item
  Raspberry Pi OS Lite - \gls{os} \emph{debian bookworm x64},
\item
  \gls{mrp} \ref{software-readout-framework}-library - Version
  \emph{1.4.1}
\item
  Unified Sensor \ref{unified-sensor}-firmware - Version \emph{1.0.1}
\end{itemize}

It can be seen that a jitter time of up to an additional \emph{1ms} is
added between the triggering of the measurements by the host system and
the receipt of the command by the sensor hardware. If the host system is
still under load, this value increases many times over. This means that
synchronising several sensors via the \gls{usb} connection alone is not
sufficient.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to \emph{secondary} mode
and synchronise the measurements based on each sync pulse received.

Since the presumed \emph{primary} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout branch
condition \emph{got pulse within 1000ms} and this becomes the
\emph{primary} sensor. This means that in a chain of sensors there is
exactly one \emph{primary} and many \emph{secondary} sensors.

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The synchronisation status can be queried via the user interface
\ref{communication-interface} using the \emph{opmode}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here was that there is no numbering or sequence of the
individual sensors.

@@

These cover all the required functions described in the usecases
\ref{usecases}. The most important difference, apart from the sensor
used, is the \emph{scan mode}. In this context, this describes whether
the sensor can measure a \emph{static} fixed point on the magnet or if
the sensor can move \emph{dynamically} around the magnet using a
controllable manipulator.

In the following, the hardware structure of a \emph{static} and
\emph{dynamic} sensor is described. For the \emph{static} sensor, only
the \emph{1D} variant is shown, as this does not differ significantly
from the structure of the \emph{1D: dual sensor}, except it uses two
\emph{TLV493D} sensors, mounted above and on top of the magnet.

@@

The electrical level here is based on a \emph{Raspberry-Pi Pico}
together with the \passthrough{\lstinline!MMC5603NJ!} magnetic sensor.
The mechanical setup consists of four 3D printed components, which are
fixed together with nylon screws to minimise possible influences on the
measurement.

Since the \emph{MMC5603NJ} only has limited measurement range of total
6uT, even small coin sized neodymium magnets already saturates the
sensor. It is possible to mount 3D printed spacers over the sensor to
increase the distance between the magnet and the sensor and thus also
measure these magnets.

@@

On the electrical side, it also consists of a \emph{SKR-Pico} stepper
motor controller, together with the \emph{TLV493D} magnetic field
sensor. This was chosen because of its larger measuring range and can
therefore be used more universally without having to change the sensor
of the arm.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of 0T to 3T with a resolution of
0.1mT. It offers an RS232 interface with a documented protocol for
connection to a \gls{pc}.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical RS232 interface. As with the other sensors, this
interface consists of your \emph{Raspberry-Pi Pico} with an additional
level shifter.

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol of the
sensor was implemented in a customized version of the
\emph{CustomSensor} class \ref{lst:CustomSensorClass}.

@@

As the following, this concept is referred to as \emph{user interaction
points} \ref{user-interaction-points} and is explained in the following
chapter.

@@

The following example shows the advantages of using the \emph{User
interaction points}:
